---
title: "Clustering_ML"
author: "BT"
date: "15/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Unsupervised ML is popular in many fields, including:

In cancer research field in order to classify patients in subgroups according their gene expression profile. This can be useful for identifying the molecular profile of patients with good or bad prognostic, as well as for understanding the disease.
In marketing for market segmentation by identifying subgroups of customers with similar profiles and who might be receptive to a particular form of advertising.
City-planning: for identifying groups of houses according to their type, value and location.

```{r}
my_data <- USArrests
my_data <- na.omit(my_data) # remove any NA values
my_data <- scale(my_data) # get all variables
install.packages("factoextra") # Install cluster package
install.packages("cluster")
library("cluster")
library("factoextra")
res.dist <- get_dist(USArrests, stand = TRUE, method = "pearson") # get distance
fviz_dist(res.dist, 
   gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07")) #get heatmap for distance
fviz_nbclust(my_data, kmeans, method = "gap_stat") # determine numbers for k-means
library("factoextra")
fviz_cluster(km.res, data = my_data, frame.type = "convex")+
  theme_minimal() # get result form kmeans
library("cluster")

pam.res <- pam(my_data, 4)
fviz_cluster(pam.res) # this is a nother way to do cluster, which is less sensitive


```

